Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-09-27 paper/main.tex
up to fiber space

\newcommand{\note}[1]{\textcolor{magenta}{#1}} 
\usepackage[nocompress]{cite}
\usepackage{hyperref} % autoref
% *** GRAPHICS RELATED PACKAGES ***
\ifCLASSINFOpdf
   \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
   \graphicspath{{./figures/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
   \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
   \graphicspath{{./figures/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
   \DeclareGraphicsExtensions{.eps}
\fi

@@

\IEEEPARstart{T}his paper uses methods from topology and category theory to develop a model of the transformation from data to graphical representation. This model provides a language to specify how data is structured and how this structure is carried through in the visualization, and serves as the basis for a functional approach to implementing visualization library components. Topology allows us to describe the structure of the data and graphics in a generalizable, scalable, and trackable way. Category theory provides a framework for separating the transformations implemented by visualization libraries from the various stages of visualization and therefore can be used to describe the constraints imposed on the library components \cite{wielsManagementEvolvingSpecifications1998,goguenCategoricalManifesto1991}. Well constrained modular components are inherently functional\cite{hughesWhyFunctionalProgramming1989}, and a functional framework yields a library implementation that is likely to be shorter, clearer, and more suitd to distributed, concurrent, and on demand tasks\cite{huHowFunctionalProgramming2015}. Using this functional approach, this paper contributes a practical framework for decoupling data processing from visualization generation in a way that allows for modular visualization components that are applicable to a variety of data sets in different formats. \note{is it OK that this is something reviewer 4 wrote}

@@

Often continuity is expressed in the choice of visual algorithm (visualization type), as explored in taxonomies by Tory and M\"{o}ller \cite{toryRethinkingVisualizationHighlevel2004} and Chi\cite{chiTaxonomyVisualizationTechniques2000}. For example, in \autoref{fig:related-work:visual-algorithm} the same table can be interpreted as a set of 1D continuous curves when visualized as a collection of line plots or as a 2D surface when visualized as an image.  This means that often there is no way to express data continuity independent of visualization type, meaning most visualization libraries will allow, for example, visualizing discrete data as a line plot or an image. General purpose visualization libraries-such as Matplotlib\cite{hunterMatplotlib2DGraphics2007}, Vtk\cite{hanwellVisualizationToolkitVTK2015,geveciVTK2012}, and D3 \cite{bostockDataDrivenDocuments2011}-carry distinct data models as part of the implementation of each visual algorithm. The lack of unified data model means that each plot in a linked\cite{beckerBrushingScatterplots1987,bujaInteractiveData1991} visualization is treated as independent, as are the transforms converting each field in the data to a visual equivalent.

Domain specific libraries can guarantee consistency because they have a single model of the data in their software design, as discussed in Heer and Agarwal \cite{HeerSoftware2006}'s survey of visualization software design patterns. For example, the relational database is core to tools influenced by APT, such as Tableau\cite{StoltePolaris2002,hanrahanVizQL2006,MackinlayShowme2007} and the Grammar of Graphics\cite{wilkinsonGrammarGraphics2005} inspired ggplot\cite{wickhamGgplot2ElegantGraphics2016a}, Vega\cite{satyanarayanDeclarativeInteractionDesign2014} and Altair\cite{vanderplasAltairInteractiveStatistical2018}. Images underpin scientific visualization tools such as Napari\cite{nicholas_sofroniew_2021_4533308} and ImageJ\cite{schneiderNIHImageImageJ2012} and the digital humanities oriented ImagePlot\cite{studiesCulturevisImageplot2021} macro; the need to visualize and manipulate graphs has spawned tools like Gephi\cite{bastianGephiOpenSource2009}, Graphviz\cite{ellsonGraphvizOpenSource2002}, and Networkx\cite{HagbergExploringNetwork2008}.

@@

The model described in this work provides a method for expressing different types of continuities and nested continuities using the same model. We obtain this generality by using the mathematical theory of fiber bundles as the basis of our abstraction, as proposed by Butler, Bryson, and Pendley\cite{butlerVisualizationModelBased1989,butlerVectorBundleClassesForm1992}. In this paper, we build on their work that proposes using topological spaces to represent different properties of data. Here we present a brief summary of topology, for more information see Hatcher\cite{hatcherAlgebraicTopology2002}, Munkres\cite{munkresElementsAlgebraicTopology1984}, and Bradley et. al. \cite{bradleyTopologyCategoricalApproach2020}.

A topological space a topological space $(X, \mathscr{T})$ is a set $X$ with a topology $\mathscr{T}$. Topologies are collections of open sets

such that the empty set and $X$ are in the collection of open sets $\mathscr{T}$, the union of elements in $\mathscr{T}$

Specifically, Butler, Bryson, and Pendley suggest that fiber bundles be the basis of an abstract data model. Fiber bundles are a collection $(\dtotal, \dbase, \dfiber, \pi)$ of topological spaces

@@

\subsection{Sheaf Maps \sheaf}
We can use sheafs to ensure continuity even when the data is broken up. Is the glue rules -> we can haz parallism. 
\begin{equation}
  \vartist: \sheaf(\dtotal) \rightarrow \sheaf(\gtotal)
  \label{eq:math:artist:artist}
\end{equation}

\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{sheaf.png}
  \caption{}
\end{figure}

@@

\begin{tikzcd}
  data \arrow[r] \arrow[d, "function"] & representation \arrow[r] & visual\;stimulus \arrow[d, "visual\;equivalent\;to\;function"] \\
  data \arrow[r]                       & representation \arrow[r] & visual\; stimulus                                          
\end{tikzcd}

\subsubsection{Category Theory}
In this work, we propose that equivariance constraints can be expressed using category theory. Vickers et. al provide a brief introduction to category theory for visualization practitioners \cite{vickersUnderstandingVisualizationFormal2013}, but their work focuses on data, representation, and evocation, while this paper is aims to provide guidance on how the map from data to representation should be implemented.

\section{Artist} 
The \textcolor{artist}{Artist $\mathcal{\vartist}$} is a transformation from data space to graphic.

\begin{equation}
  \vartist: \dtotal \rightarrow \gtotal
  \label{eq:math:artist:artist}
\end{equation}

We propose that the artist $\mathcal{\vartist}$ is a morphism of presheaves defined to be a natural transformation (\autoref{sec:related-work:category-theory})
\note{commutative diagram maybe?}

We can then explain inclusion & continuity as special cases, preservation as consequence of this. Generalize inclusion of open sets and restriction (how topology is put together) and equivariance on the fiber in terms of natural transformations <- condition we want to satisfy is natural transformation. Constraint on artist is that it's a natural transformations, will construct that way, will show

To show that the artist is a natural transformation, we first define the categories $\mathcal{E}$ and $\mathcal{H}$. In order to define these categories, we introduce the category of open sets $\mathcal{K}$

\begin{definition} The category $\mathcal{K}$ consists of 
  \begin{itemize}
    \item \textit{objects} all open sets $U_{i} \in \{U\}$ in \dbase, including the empty set $\varnothing$ and the maximum set \dbase
    \item \textit{morphisms} inclusion maps from a subspace to a larger space $\iota: U_{i} \hookrightarrow U_{j}$, which is equivalent to $U_{i} \subseteq U_{j}$ and  
  \end{itemize} 
\end{definition}

The open set objects $U_{i}$ are used to track subsets of the data defined globally on \dbase. For example,

\begin{definition} For each open set object $U_{i}$ of category $\mathcal{K}$, there is a set $\Gamma(U_i, \dtotal)$. The elements of this set are the sections $\{\dsection^{0},\cdots, \dsection^{i}, \dsection^{n}\}$ of \dtotal\ over open set $\U_{i}$. The sections $\Gamma(\dbase, \dtotal)$ are called the global sections of $\dtotal$. \cite{SheafMathematics2021,spanier1989algebraic}.
\end{definition}

Each section is how we represent a unique dataset, where the set of sections $\Gamma$ is the set of all datasets that have the same data fields \dfiber\ and continuity \dbase\. For example, database tables that have the same schema and discrete index \cite{spivakSIMPLICIALDATABASES}.

\begin{definition} The category $\mathcal{\E}$ consists of 
  \begin{itemize}
    \item\textit{objects} the presheaf $F:

    \item\textit{morphisms} inclusion maps: $\iota: E_i \hookrightarrow E_j$
  \end{itemize}
\end{definition}

\begin{definition} 
\end{definition}

\subsection{Data}
We model data as sections of a fiber bundle $(\dtotal, \pi, \dbase, \dfiber)$. We encode the continuity of the data as the \textcolor{base}{base space} $\dbase$. \note{does this go in intro? The \textcolor{fiber}{fiber space} \dfiber\ is the space of all possible values of the data \autoref{eq:related-work:fiber}. We model the data as the section \dsection because, as described in \autoref{sec:related-work:fiber-bundles}, the section is the map from the indexing space \dbase to the space of possible data values \dfiber. Spivak's notation, as discussed in \autoref{sec:related-work:equivariance}, also allows for associating elements in a section with the field it comes from. This allows for field based selection of values, while inclusion allows for continuity (index) based selections.

@@

\begin{LaTeXdescription}
\item [\textcolor{base}{base space} \gbase] continuity of display space (e.g. screen, 3D print)
\item [\textcolor{fiber}{fiber space} \gfiber] attributes of the display space (e.g a pixel = (x,y,r,g,b,a))
\end{Latex}
\item [\textcolor{section}{section} \gsection] graphic generating function
\end{LaTeXdescription}.

@@

\section{Constraints: Construction and formal properties of Artists}
\begin{figure*}[h!]
  \includegraphics[width=\linewidth]{q.png}
  \caption{}
  \label{fig:constraints:q-overall}
\end{figure*}

@@

\begin{definition} We define the \textcolor{artist}{Artist} natural transformation \vartist\ as the tuple $(\vindex, \vchannel, \vmark, \dtotal, \vtotal, \gtotal)$ where
  \begin{enumerate}
    \item \vindex\ is a continuity preserving functor
    \item \vchannel\ and \vmark\ are equivariance preserving functors
    \item \dtotal, \vtotal, and \gtotal\ are profunctor categories of sheafs (\autoref{def:artist:profunctor})
  \end{enumerate}
\end{definition}

@@

@@

\section{Case Study}
\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{path_of_q.png}
    \caption{\note{add in xi!}}
  \label{fig:api}
\end{figure}
We implement the \textbf{arrows} in \autoref{fig:api}. \mintinline{python}{axesArtist} is a parent artist that acts as a screen. This allows for the composition described in                                           \autoref{sec:artist:union}

>>>>

\newcommand{\note}[1]{\textcolor{magenta}{#1}} 
\usepackage[nocompress]{cite}
\usepackage[]{footmisc}
\usepackage{hyperref} % autoref
% *** GRAPHICS RELATED PACKAGES ***
\ifCLASSINFOpdf
   \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
   \graphicspath{{./figures/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
   \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
   \graphicspath{{./figures/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
   \DeclareGraphicsExtensions{.eps}
\fi

@@

\IEEEPARstart{T}his paper uses methods from topology and category theory to develop a model of the transformation from data to graphical representation. This model provides a language to specify how data is structured and how this structure is carried through in the visualization, and serves as the basis for a functional approach to implementing visualization library components. Topology allows us to describe the structure of the data and graphics in a generalizable, scalable, and trackable way. Category theory provides a framework for separating the transformations implemented by visualization libraries from the various stages of visualization and therefore can be used to describe the constraints imposed on the library components \cite{wielsManagementEvolvingSpecifications1998,goguenCategoricalManifesto1991}. Well constrained modular components are inherently functional\cite{hughesWhyFunctionalProgramming1989}, and a functional framework yields a library implementation that is likely to be shorter, clearer, and more suited to distributed, concurrent, and on demand tasks\cite{huHowFunctionalProgramming2015}. Using this functional approach, this paper contributes a practical framework for decoupling data processing from visualization generation in a way that allows for modular visualization components that are applicable to a variety of data sets in different formats. \note{is it OK that this is something reviewer 4 wrote}

@@

 The preservation of continuity can be made explicit, as in the transformation of table to parallel coordinates in Ruchikachorn and Mueller \cite{ruchikachornLearningVisualizationsAnalogy2015}, but is often expressed implicitly in the choice of visual algorithm (visualization type), as explored in taxonomies by Tory and M\"{o}ller \cite{toryRethinkingVisualizationHighlevel2004} and Chi\cite{chiTaxonomyVisualizationTechniques2000}.

For example, in \autoref{fig:related-work:visual-algorithm} the same table can be interpreted as a set of 1D continuous curves when visualized as a collection of line plots or as a 2D surface when visualized as an image.  This means that often there is no way to express data continuity independent of visualization type, meaning most visualization libraries will allow, for example, visualizing discrete data as a line plot or an image. General purpose visualization libraries-such as Matplotlib\cite{hunterMatplotlib2DGraphics2007}, Vtk\cite{hanwellVisualizationToolkitVTK2015,geveciVTK2012}, and D3 \cite{bostockDataDrivenDocuments2011}-carry distinct data models as part of the implementation of each visual algorithm. The lack of unified data model means that each plot in a linked\cite{beckerBrushingScatterplots1987,bujaInteractiveData1991} visualization is treated as independent, as are the transforms converting each field in the data to a visual equivalent.

Domain specific libraries can often guarantee consistency because they have a single model of the data in their software design, as discussed in Heer and Agarwal \cite{HeerSoftware2006}'s survey of visualization software design patterns. For example, the relational database is core to tools influenced by APT, such as Tableau\cite{StoltePolaris2002,hanrahanVizQL2006,MackinlayShowme2007} and the Grammar of Graphics\cite{wilkinsonGrammarGraphics2005} inspired ggplot\cite{wickhamGgplot2ElegantGraphics2016a}, Vega\cite{satyanarayanDeclarativeInteractionDesign2014} and Altair\cite{vanderplasAltairInteractiveStatistical2018}. Images underpin scientific visualization tools such as Napari\cite{nicholas_sofroniew_2021_4533308} and ImageJ\cite{schneiderNIHImageImageJ2012} and the digital humanities oriented ImagePlot\cite{studiesCulturevisImageplot2021} macro; the need to visualize and manipulate graphs has spawned tools like Gephi\cite{bastianGephiOpenSource2009}, Graphviz\cite{ellsonGraphvizOpenSource2002}, and Networkx\cite{HagbergExploringNetwork2008}.

@@

The model described in this work provides a method for expressing different types of continuities and nested continuities using the same model. We obtain this generality by using the mathematical theory of fiber bundles as the basis of our abstraction, as proposed by Butler, Bryson, and Pendley\cite{butlerVisualizationModelBased1989,butlerVectorBundleClassesForm1992}. In this paper, we build on their work that proposes using topological spaces to represent different properties of data.

Specifically, Butler, Bryson, and Pendley suggest that fiber bundles be the basis of an abstract data model. Fiber bundles are a collection of topological spaces. 
\begin{definition}
A topological space $(X, \mathscr{T})$ is a set $X$ with a topology $\mathscr{T}$. Topologies are collections of open sets $U$ such that the empty set and $X$ are in the collection of open sets $\mathscr{T}$, the union of elements in $\mathscr{T}$ \note{finish out this definition}
\end{definition}

Here we present a very brief summary of topics, for more information see Hatcher\cite{hatcherAlgebraicTopology2002}, Munkres\cite{munkresElementsAlgebraicTopology1984}, and Bradley et. al. \cite{bradleyTopologyCategoricalApproach2020}.

@@

@@

\subsubsection{Category Theory}
\label{sec:related-work:equivariance:category}
In this work, we propose that equivariance constraints can be expressed using category theory. Vickers et. al provide a brief introduction to category theory for visualization practitioners \cite{vickersUnderstandingVisualizationFormal2013}, but their work focuses on data, representation, and evocation, while this paper is aims to provide guidance on how the map from data to representation should be implemented.

\section{Artist} 
The \textcolor{artist}{Artist} $\mathcal{\vartist}$\footnote{We call this transformation the artist because the Artist object in Matplotlib\cite{hunterMatplotlib2DGraphics2007} is responsible for converting data to a prerender graphical object} is a transformation from data  $\mathcal{\dtotal}$ to graphic $\mathcal{\gtotal}$.

\begin{equation}
  \vartist: \mathcal{\dtotal} \rightarrow \mathcal{\gtotal}
  \label{eq:math:artist:artist}
\end{equation}

We formally define data and graphic as the categories $\mathcal{\dtotal}$ and $\mathcal{\gtotal}$. To explain these categories, we first define the category of open sets $\mathcal{\dbase}$ and the category of fiber spaces $\mathcal{\dfiber}$.

\begin{definition} The category $\mathcal{\dbase}$ consists of 
  \begin{itemize}
    \item \textit{objects} all open sets $U_{i} \in \{U\}$ in \dbase, including the empty set $\varnothing$ and the maximum set \dbase
    \item \textit{morphisms} inclusion maps from a subspace to a larger space $\iota: U_{i} \hookrightarrow U_{j}$, which is equivalent to $U_{i} \subseteq U_{j}$ and  
  \end{itemize} 
\end{definition}

The objects $U_{i}$ are a way to manage subsets of the data. For example, let there be a data value for each point along the interval $\dbase=\right[0,1\left]$. Since this function is continuous, there is a subset of the data defined along the open set $U_{a} = \right(0.2, 0.4\left)$. The open set $U_{a}$ provides a unique way of identifying that subset.

\note{maybe a small image here or when we introduce open sets showing what we mean?}

\begin{definition} For each open set object $U_{i}$ of category $\mathcal{\dbase}$, there is a set $\Gamma(U_i, \dtotal)$. The elements of this set are the sections $\{\tau^{j}:U_i \rightarrow \dfiber_{U_{i}}\}_{j\in I}$ of \dtotal\ over open set $\U_{i}$. The sections $\Gamma(\dbase, \dtotal)$ are called the global sections of $\dtotal$. \cite{SheafMathematics2021,spanier1989algebraic}.
\end{definition}

Each section is how we represent a unique dataset, where the set of sections $\Gamma$ is the set of all datasets that have the same data fields in the \dfiber\ and continuity as encoded in\dbase\. For example, database tables that have the same schema and discrete index, as illustrated in Spivak \cite{spivakSIMPLICIALDATABASES}.

\begin{definition} The fiber space category $\mathcal{\dfiber}$ is a category of sets \textbf{Set}. This means its objects are sets, and its morphisms are total functions\cite{barrCategoryTheoryComputing}
\end{definition}

\begin{definition} The monad $T$ is [a,b,c]

For example, these functions could be the binary operations, group actions, and measurement scales discussed in \autoref{sec:related-work:equivariance}. These functions could also be monoid actions, which are a way of applying partial order relations to data\cite{fongInvitationAppliedCategory2019}, such as to build multi-ranked indicators\cite{bruggemannRankingPrioritizationMultiindicator2011}
}

\begin{definition} The category $\mathcal{\dtotal}$ consists of 
  \begin{itemize}
    \item\textit{object} the space of continuous\footnote{or piecewise continuous}sections $\sheaf: U_{i} \rightarrow \Gamma(U_{i}, \dtotal) $ which is a sheaf\cite{spanier1989algebraic,SheafMathematics2021}. 
    \item\textit{morphisms} bundle maps E, E, fiber to itself and is the fiber map allowable, functions F to itself forms a monoid (one object category), F and it's allowable maps form a category, monoid could be monotonic functions, group actions, extending that to bundle E, interested in E to itself, which when restricted to fiber are category maps of fiber to itself, maps from sheaf to itself, that when restricted to fiber gives you fiber to itself, given bundle map E->E, then you can show that you have a sheaf map... Given E->E, and F->F, then there's a map from one sheaf to another. bundle map induces on level of sections induces on sheafs -> part of the definition of the presheaf

  \end{itemize}
\end{definition
The functions on the data

\note{equivariance is a special case of functions}
\note{actions are a special case of actions}
\begin{definition} category of bundle maps, which include category of fiber maps, what are allowable of fiber to itself, ex translation and scales only ..., objects are a fiber, maps are fiber to fiber defined as their own category, E to V fibers changes

zooming is inclusion maps on both sides 
\end{definition}

The objects of the data category $\mathcal{\dtotal}$ and graphic category $\mathcal{\gtotal}$ are the sheaves $\Gamma(\dbase, \dtotal)$ and $\Gamma(\gbase, \gtotal)$. An alternate notation is $\sheaf(\dtotal)$ and $\sheaf(\gtotal)$. The artist is a morphism of sheafs $\sheaf(\dtotal)$ to $\sheaf(\gtotal)$, which means it is by definition a natural transform\cite{SheafMathematics2021}. As mentioned in \autoref{sec:related-work:equivariance:category}

that the artist $\vartist$ transforms functions that act on data $f:\dtotal\rightarrow \dtotal$ to functions that act on graphics $\g: \gtotal\rightarrow \dtotal$ in a way in which the following diagram commutes 
\begin{tikzcd}
  \mathcal{\dtotal} \arrow[r, "\vartist"] \arrow[d, "f"] & \mathcal{\gtotal} \arrow[d, "g"] \arrow[d, "\ca"] \\
  \mathcal{\dtotal} \arrow[r, "\vartist"]                & \mathcal{\gtotal}                                
\end{tikzcd}
meaning that, as described in \autoref{sec:related-work:equivariance}, the artist \vartist is constructed such that $\vartist(f(\dtotal)) = g(\vartist(\dtotal))$, meaning a transformation of the data has a consistent equivalent transformation of the graphic. In \autoref{sec:artist:construction}, we show a method of constructing the artist such that continuity and equivariance are preserved. We then use this formulation to guide the development of visualization library components in \autoref{sec:case-study}.

\subsection{Data}
We model data as sections of a fiber bundle $(\dtotal, \pi, \dbase, \dfiber)$. We encode the continuity of the data as the \textcolor{base}{base space} $\dbase$. \note{does this go in intro?} The \textcolor{fiber}{fiber space} \dfiber\ is the space of all possible values of the data \autoref{eq:related-work:fiber}. We model the data as the section \dsection because, as described in \autoref{sec:related-work:fiber-bundles}, the section is the map from the indexing space \dbase to the space of possible data values \dfiber. Spivak's notation, as discussed in \autoref{sec:related-work:equivariance}, also allows for associating elements in a section with the field it comes from. This allows for field based selection of values, while inclusion allows for continuity (index) based selections.

@@

\begin{LaTeXdescription}
\item [\textcolor{base}{base space} \gbase] continuity of display space (e.g. screen, 3D print)
\item [\textcolor{fiber}{fiber space} \gfiber] attributes of the display space (e.g a pixel = (x,y,r,g,b,a))
\item [\textcolor{section}{section} \gsection] graphic generating function
\end{LaTeXdescription}.

@@

\section{Constraints: Construction and formal properties of Artists}
\label{sec:artist:construction}
\begin{figure*}[h!]
  \includegraphics[width=\linewidth]{q.png}
  \caption{}
  \label{fig:constraints:q-overall}
\end{figure*}

@@

\begin{definition} We define the natural transformation \textcolor{artist}{Artist}  \vartist\ as the tuple $(\vindex, \vchannel, \vmark, \mathcal{\dtotal},\mathcal{\vtotal}, \mathcal{\gtotal})$ where
  \begin{enumerate}
    \item \vindex\ is a continuity preserving functor
    \item \vchannel\ and \vmark\ are equivariance preserving functors
    \item $\mathcal{\dtotal}$, $\mathcal{\vtotal}$, and $\mathcal{\gtotal}$ are profunctor categories of sheafs
    \item 
  \end{enumerate}
\end{definition}

@@

The functor $\vindex$ is a deformation retract, which means....\cite{hatcherAlgebraicTopology2002,spanier1989algebraic}

@@

\section{Case Study}
\label{sec:case-study}
\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{path_of_q.png}
    \caption{\note{add in xi!}}
  \label{fig:api}
\end{figure}
We implement the \textbf{arrows} in \autoref{fig:api}. \mintinline{python}{axesArtist} is a parent artist that acts as a screen. This allows for the composition described in                                           \autoref{sec:artist:union}
